03 Data Vizualization

### 2022-04-06 03_data_viz.Rmd
Update 03_data_viz.Rmd

```{r}
# Sourced Functions
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromeleon.R"))
source(file.path("libs", "error_prop.R"))
source(file.path("libs", "calculate_turnover.R"))
`%nin%` = Negate(`%in%`) # "Not In" function
var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
```

@@

lit_turnover_w_ours <- lit_turnover %>% bind_rows(turnover_means)
```

@@

```{r}
p_tax_FA <- fatty_acids_wide_with_tax %>% 
  select(-ID) %>% 
  # Remove Fungi from this plot
  filter(phylum != "Fungi") %>% 
  pivot_longer(cols = -phylum, 
               names_to = "FA",
               values_to = "rel_abund") %>%
  ggplot(aes(x = FA, 
             y = rel_abund,
             color = phylum)) +
  #stat_pointinterval(point_interval = "mean_qi") +
  geom_boxplot(
    outlier.shape = NA,
    alpha = 0.1
    ) +
  facet_wrap(vars(phylum), nrow = 1) +
  scale_color_futurama() +
  labs(y = "Relative Abundance",
       x = "",
       color = "Phylum") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1),
        panel.grid = element_blank(),
        strip.background = element_blank(),
        legend.position = "NA",
        strip.text = element_text(size = 16)
        # legend.background = element_rect(
        #                           size=0.5, 
        #                           linetype="solid", 
        #                           colour ="black")
        )

@@

## Compound abundance vs. turnover

```{r}
gen_calc_data %>% 
  filter(inc_time_d != 0) %>% 
  ggplot(aes(x = rel_area_FID,
             y = u_d)) +
  geom_point(aes(color = chain_fctr)) +
  scale_color_viridis_d(option = "plasma") +
  facet_wrap(~terrain) +
  labs(x = "Relative Area (GC-FID)",
       y = TeX("$Turnover (d^{-1})$"),
       color = "Compound class") +
  theme_bw() +
  theme(panel.grid = element_blank(),
        strip.background = element_blank())
```

## Meta analysis of turnover rates reported in literature

```{r}
# Import lit search data
lit_turnover <- read_xlsx(file.path("data", "literature_turnover_rates.xlsx"))
lit_turnover <- lit_turnover %>% 
  # Arrange by turnover time
  arrange(u_d_mn) %>% 
  # Reassign n values
  mutate(n = seq(from = 1, to = nrow(lit_turnover)))

# Our summarized data
gen_calc_mini <- gen_calc_data_summarized %>% 
  # Calculate mean per terrain per inc time
  group_by(inc_time_d, terrain) %>% 
  summarize(u_d_mn = mean(u_d, na.rm = TRUE),
            u_d_max = max(u_d),
            u_d_min = min(u_d)) %>%
  # Calculate mean of means (combine inc_times)
  group_by(terrain) %>% 
  summarize(u_d_mn = mean(u_d_mn, na.rm = TRUE),
            u_d_max = max(u_d_mn, na.rm = TRUE),
            u_d_min = min(u_d_mn, na.rm = TRUE)) %>% 
  # Rename to match `lit_turnover` tibble
  arrange(u_d_mn) %>% 
  mutate(method = "2H Lipid SIP",
         method_type = "2H-Lipid-SIP",
         n = c(17, 18, 19),
    soil_type = case_when(
      terrain == "Niwot Ridge Tundra" ~ "tundra",
      terrain == "Gordon Gulch Conifer Forest" ~ "conifer forest",
      terrain == "Marshall Mesa Grassland" ~ "grassland")
  )
# Add in our data! ^_^
lit_turnover_w_ours <- lit_turnover %>% bind_rows(gen_calc_mini)

lit_turnover_w_ours <- lit_turnover_w_ours %>% 
  mutate(
    source = case_when(
      method == "2H Lipid SIP" ~ "This study",
      TRUE ~ "Literature values"
  )) %>% 
  # Add in generation times of u_d mean value
  left_join(summarized_weighted_gen_d, by = "terrain") %>% 
  mutate(gen_d_weighted = case_when(
    is.na(gen_d_weighted) ~ log(2)/u_d_mn,
    TRUE ~ gen_d_weighted
    )
  )
```

@@

```{r lit rates}
literature_values_swatch <- c("#4ebad5", "#88e3cf", "#e388d7", "#ffb1ad")

p_lit_turnover_w_ours <- lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(
    aes(x = -n,
        y = u_d_mn,
        fill = method_type
        )
    ) +
  geom_col() +
  coord_flip(ylim = c(0, 0.5)) +
  scale_fill_manual(values = literature_values_swatch) +
  labs(y = TeX("Turnover (d$^{-1}$)"),
       fill = "Method") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 0, hjust = 0.5, size = 14),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 18),
        #legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        legend.position = c(0.85, 0.1),
        legend.text = element_text(size = 15),
        legend.title = element_blank())
p_lit_turnover_w_ours

@@

```{r}
# By terrain  
lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(aes(x = n, 
             y = u_d_mn,
             color = soil_type)) +
  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
               color = "black") +
  geom_point(size = 3) +
  scale_color_npg() +
  geom_label(label = "This study",
            x = 18,
            y = 0.13,
            color = "black") +
  geom_label(label = "Literature values",
            x = 9,
            y = 0.6,
            color = "black") +
  #scale_y_log10() +
  #annotation_logticks(sides = "l") +
  coord_cartesian(
    xlim = c(0, 20),
    ylim = c(0, 0.80), 
    expand = FALSE) +
  labs(y = "Mean Turnover Time (d^-1)",
       color = "Soil Source") +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "bottom")
## With log scale
lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(aes(x = n, 
             y = u_d_mn,
             color = soil_type)) +
  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
               color = "black") +
  geom_point(size = 3) +
  scale_color_npg() +
  geom_label(label = "This study",
            x = 18,
            y = 0.10,
            color = "black") +
  geom_label(label = "Literature values",
            x = 9,
            y = 0.35,
            color = "black") +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  labs(y = "Mean Turnover Time (d^-1)",
       color = "Soil Source") +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "bottom")
```

```{r}
lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(aes(x = n, 
             y = u_d_mn,
             color = soil_type)) +
  geom_segment(aes(y = 0, yend = u_d_mn, xend = n),
               color = "black") +
  geom_point(size = 3) +
  scale_color_npg() +
  geom_label(aes(
    x = 9,
    y = 0.4),
            label = "Literature values",
            color = "black") +
  geom_label(aes(
    x = 18,
    y = .1),
             label = "This study",
             color = "black") +
  scale_y_log10() +
  annotation_logticks(sides = "l") +
  labs(y = TeX("Mean turnover rate ($d^{-1}$)"),
       color = "Soil Source") +
  theme_classic() +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank(),
        axis.title.x = element_blank(),
        legend.position = "bottom")
```

```{r}
p_lit_turnover_across_method <- lit_turnover_w_ours %>%
  # order by mean turnover rate
  ggplot(aes(y = n, 
             x = u_d_mn,
             color = source)) +
  geom_segment(aes(x = 0, xend = u_d_mn, yend = n),
               color = "black") +
  geom_point(size = 3) +
  geom_text_repel(aes(label = method),
                  color = "black",
                  size = 3.5,
                  segment.color = NA,
                  nudge_x = 1,
                  segment.curvature = -0.1,
                  segment.angle = -20,
                  segment.ncp = 3,
                  segment.size = 0.1) +
  scale_color_manual(values = c("#000000", "#1986bd")) +
  #scale_x_log10(breaks = c(0.01, 0.05, 0.1, 0.5)) +
  #annotation_logticks(sides = "b") +
  scale_x_continuous(sec.axis = sec_axis(trans = ~ log(2)/.,
                                         breaks = c(1, 3, 5, 7, 14, 30, 365),
                                         labels = c("1 Day", "3 Days", "5 Days", "1 Week", "2 Weeks", "1 Month", "1 Year"),
                                         name = "Generation time")) +
  coord_cartesian(xlim = c(0, 0.8), ylim = c(0, 20), expand = FALSE) +
  labs(x = TeX("Mean turnover rate ($d^{-1}$)"),
       color = "Source") +
  theme_classic() +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank(),
        axis.title.y = element_blank(),
        legend.position = "bottom",
        axis.text.x.top = element_text(angle = 30, hjust = 0)
        )

p_lit_turnover_across_method
```

```{r}
cowplot::save_plot(filename = "fig_output/p_lit_turnover_across_method.png",
          plot = p_lit_turnover_across_method,
          base_height = 6,
          base_width = 8)
```

@@

## Turnover versus abundance

```{r}
p_turnover_vs_abundance <- gen_calc_data %>% 
  ggplot(
    aes(x = u_d,
        y = compound_ug_ext,
        color = terrain
    )
  ) +
  geom_point(alpha = 0.5) +
  scale_color_manual(values = terrain_color_swatch) +
  facet_wrap(vars(terrain)) +
  labs(
    x = TeX("Turnover rate ($d^{-1}$)"),
    y = "Extracted compound mass (µg)"
  ) +
  theme_bw() +
  theme(
    legend.position = "none",
    strip.background = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )

save_plot(
  filename = "fig_output/p_turnover_vs_abundance.pdf", 
  plot = p_turnover_vs_abundance,
  base_height = 3,
  base_width = 7
  )
```

@@

## Assimilation efficiency error propagation

```{r}
p_gen_calc_errorprop <- gen_calc_errorprop %>%
  mutate(u_d = case_when(
    is.na(u_d) ~ 0,
    TRUE ~ u_d
  )) %>% filter(inc_time_d_str != "0 Days") %>% 
  ggplot(aes(x = a,
             y = u_d,
             color = compound,
             group = compound)) +
    geom_smooth(method = "lm",
                formula = "y~x") +
  facet_wrap(vars(terrain, inc_time_d_str),
             ncol = 2) +
  labs(x = "Assimilation efficiency (a)",
       y = TeX("Turnover rate ($d^{-1}$)"),
       color = "Compound"
       ) +
  theme_bw()

p_gen_calc_errorprop
```

```{r cowplot moo}
save_plot(filename = "fig_output/p_gen_calc_error_prop.pdf",
          plot = p_gen_calc_errorprop,
          base_height = 12,
          base_width = 8
          )
```

>>>>

```{r}
# Sourced Functions
source(file.path("libs", "visualization.R"))
source(file.path("libs", "chromeleon.R"))
source(file.path("libs", "error_prop.R"))
source(file.path("libs", "calculate_turnover.R"))
source(file.path("libs", "turnover_to_gen.R"))
`%nin%` = Negate(`%in%`) # "Not In" function
var_to_str = function(v) {return(deparse(substitute(v)))} # Convert variable name to string
```

@@

lit_turnover_w_ours <- lit_turnover %>% bind_rows(turnover_means) %>% 
  # Convert to generation time:
  mutate(gen_d = turnover_to_gen(u_d_mn))
```

@@

```{r}
p_tax_FA <- fatty_acids_wide_with_tax %>% 
  select(-ID) %>% 
  # Remove Fungi from this plot
  filter(phylum != "Fungi") %>% 
  pivot_longer(cols = -phylum, 
               names_to = "FA",
               values_to = "rel_abund") %>%
  ggplot(aes(x = FA, 
             y = rel_abund,
             color = phylum)) +
  #stat_pointinterval(point_interval = "mean_qi") +
  geom_boxplot(
    outlier.shape = NA,
    alpha = 0.1
    ) +
  facet_wrap(vars(phylum), nrow = 1) +
  scale_color_manual(values = c("#E41A1C", "#377EB8", "#4DAF4A", "#984EA3", "#A65628", "#FF7F00", "#F781BF", "#999999")) +
  labs(y = "Relative Abundance",
       x = "",
       color = "Phylum") +
  theme_bw() +
  theme(axis.text.x = element_text(angle = 90,
                                   hjust = 1),
        panel.grid = element_blank(),
        strip.background = element_blank(),
        legend.position = "NA",
        strip.text = element_text(size = 16)
        # legend.background = element_rect(
        #                           size=0.5, 
        #                           linetype="solid", 
        #                           colour ="black")
        )

@@

@@

```{r lit rates}
literature_values_swatch <- c("#4ebad5", "#88e3cf", "#e388d7")
literature_values_swatch_2 <- c("#26AFE1", "#6269EB", "#E0187B")

p_lit_turnover_w_ours <- lit_turnover_w_ours %>%
  filter(method_type != "Microscopy") %>% 
  # order by mean turnover rate
  ggplot(
    aes(x = -n,
        y = u_d_mn,
        fill = method_type,
        label = round(gen_d, 1)
        )
    ) +
  geom_col() +
  geom_text(nudge_y = 0.05, size = 2) +
  coord_flip(ylim = c(0, 0.5)) +
  scale_fill_manual(values = literature_values_swatch_2) +
  labs(y = TeX("Turnover (d$^{-1}$)"),
       fill = "Method") +
  theme_classic() +
  theme(axis.title.y = element_blank(),
        axis.text.x = element_text(angle = 0, hjust = 0.5, size = 14),
        axis.ticks.y = element_blank(),
        axis.text.y = element_blank(),
        axis.title.x = element_text(size = 18),
        #legend.position = "bottom",
        plot.title = element_text(hjust = 0.5),
        legend.position = c(0.85, 0.1),
        legend.text = element_text(size = 15),
        legend.title = element_blank(),
        plot.margin = margin(1,1,1.5,1.2, "in"))
p_lit_turnover_w_ours

@@

@@

@@
